STA304 Paper #1

### 2022-02-06 outputs/paper/paper.Rmd
Created template to follow and chosen dataset for paper 1

---
title: "STA304 Paper #1"
subtitle: "My subtitle if needed"
author: "Ziyao Han"
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point).

@@

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

@@

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

\appendix

# Appendix {-}

# Additional details

>>>>

---
title: "STA304 Paper #1"
subtitle: "My subtitle if needed"
author: "Ziyao Han"
thanks: "Code and data are available at: https://github.com/HanFrank/STA304-Paper-1"
date: "February 6, 2022"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output: 
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(knitr)
```

@@

First Paragraph is going to be motivational and broad.

Second Paragraph is about what was done and what was found.

Third paragraph is about implications.

Final Paragraph about the remainder of the paper.

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by [@citeTidy] If we were interested in baseball data then could be useful. [@citebookdown] also [@citeknitr] data [@citeodt]

@@

Paragraph or two introducing the dataset broadly.

Then show an extract of the dataset (Table \@ref(tab:extract)).

```{r extract, echo = FALSE, warning = FALSE, message = FALSE}
monthly_shelter_usage <- read_csv(here::here("inputs/data/filler_data.csv"))

monthly_shelter_usage %>%
  select(population_group, returned_from_housing) %>%
  slice(1:10) %>%
  kable(
    caption = "First ten rows of a dataset that shows shelter usage",
    col.names = c("Population Group", "Number returned from housing"),
    digits = 1,
    booktabs = TRUE,
    linesep=""
  )
```

Paragraph or two more about it

@@

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}
# This needs to be about the random data that I sampled?
```

@@

@@

@@
